\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')


\usepackage[sorting = ydnt,defernumbers,maxbibnames=99]{biblatex}
\defbibheading{bibliography}{}
\AtBeginBibliography{\small}
\addbibresource{publications.bib}

\include{reversebibnum}

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{black}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'

% character encoding
\usepackage[utf8]{inputenc}  

% adjust the page margins
\usepackage{geometry}
\geometry{left=2.2cm,right=2.2cm,top=2.2cm,bottom=2.2cm}


% personal data
\name{Dr Filippo}{Pecci}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
%\address{Department of Civil and Environmental Engineering, Imperial College London }{Skempton Building, South Kensington Campus}{London SW7 2Az}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
%\phone[mobile]{+447474765482}                   % optional, remove / comment the 
\email{fp0820@princeton.edu} 

\homepage{filippopecci.github.io}                         % 
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle

%\section{Current position}
%\cventry{2018-preset}{Department of Civil and Environmental %Engineering}{Research Associate}{Imperial College London}{}{}
\section{Research Experience}
\cventry{2022--present}{Andlinger Center for Energy and the Environment}{Associate Research Scholar}{Princeton University}{}{\vspace{0.1cm}
\begin{itemize}
\item Working at ZERO Lab on optimization methods for capacity expansion models of Macro-Energy Systems
%\item Technical supervision of $5$ PhD students working on different optimization and water engineering problems;
%\item Responsible for writing reports and presenting research results to industrial funders and partners;
%\item Participation in series of cross-departmental seminars on optimization and control;
%\item Research resulted in $8$ publications in peer-reviewed scientific journals;
%\item Responsible for writing reports and presenting research results to industrial funders and partners;
%\item Participation in conferences in water engineering, optimization, and control.
\end{itemize}}
\cventry{2018--2022}{Department of Civil and Environmental Engineering}{Research Associate, Computational optimization}{Imperial College London}{}{
\vspace{0.1cm}
\begin{itemize}
\item Fundamental research into tailored optimization algorithms to solve large scale single and multi-objective mixed-integer non-linear problems for optimal design and operation of water systems;
%\item Development of optimization tools for optimal network design, control, model identification, and fault estimation in water systems;
%\item Technical supervision of $5$ PhD students working on different optimization and water engineering problems;
%\item Responsible for writing reports and presenting research results to industrial funders and partners;
%\item Participation in series of cross-departmental seminars on optimization and control;
%\item Research resulted in $8$ publications in peer-reviewed scientific journals;
%\item Responsible for writing reports and presenting research results to industrial funders and partners;
%\item Participation in conferences in water engineering, optimization, and control.
\end{itemize}
}

\section{Qualifications}
\cventry{2014--2018}{Department of Civil and Environmental Engineering}{PhD in Computational optimization}{Imperial College London}{}{\cvitem{Thesis}{Optimal design-for-control of water supply networks by mixed integer programming}
\begin{itemize} 
\item Modelling and analysis of large scale water distribution networks;
\item Novel tailored global optimization methods to solve mixed integer nonlinear programs for optimal design-for-control of water distribution networks;
\item Application of mathematical optimization methods to multi-objective optimal design-for-control problems in water distribution networks;
%\item Research resulted in $5$ publications in peer-reviewed scientific journals.
\end{itemize}
}
\vspace{0.1cm}

% arguments 3 to 6 can be left empty
\cventry{2011--2014}{Department of Mathematics}{MSc in Mathematics}{Universita' degli studi di Padova}{}{Emphasis on PDEs, stochastic analysis, applied linear algebra, computational methods.\\ \cvitem{Thesis}{Hierarchical Stratifications of Pareto Sets}}
\vspace{0.1cm}
\cventry{2008--2011}{Department of Mathematics}{BSc in Mathematics}{Universita' degli studi di Padova}{}{}


%\clearpage
\section{Teaching Experience}
\cventry{2014-present}{Department of Civil and Environmental Engineering}{Lecturing and tutorials}{Imperial College London}{}{\begin{itemize}%
\item Lectures for BSc modules on convex optimization with applications in optimal reservoir control, and parameter estimation in water distribution networks.
\item Tutorials on applications of convex optimization to problems in image in-painting, optimal control, machine learning, and hydraulic model calibration.
\item Lectures and tutorials for MSc modules on modelling and optimization of water distribution networks.
\item Small-group tutorials on mathematics for MSc students, with focus on linear algebra and calculus;
\item Graduate Teaching Assistant for MSc modules in Hydroinformatics and Water distribution and Distribution.
\end{itemize}}
\cventry{2014-present}{Department of Civil and Environmental Engineering}{Supervision}{Imperial College London}{}{\begin{itemize}
\item Technical supervision of $5$ PhD students working on optimal design, model identification and fault estimation problems for water distribution networks.
\item Co-supervision of $4$ final year MSc projects on analysis and optimization of water distribution networks.   
\end{itemize}}

% \section{Programming Skills}
% \cvdoubleitem{Programming}{Matlab, Python}{Optimization packages}{Gurobi, Cplex,\\ Mosek, Ipopt, Baron}

% \section{Computing, Languages}
% \cvitem{Programming}{Julia, Matlab, Python}
% \cvitem{optimization packages}{CVXPY, JuMP, Ipopt, Mosek, Gurobi, Cplex, Baron}
% \cvitem{Languages}{English: Fluent}{$\qquad \qquad \quad \;$ Italian : Mother tongue}



% \section{Referees}
% \begin{cvcolumns}
%   \cvcolumn{Dr Ivan Stoianov}{Senior Lecturer in Water Systems Engineering\\ Department of Civil and Environmental Engineering\\ 
%   Imperial College London\\
%   Skempton Building \\
%   South Kensington Campus\\
%   London, SW7 2AZ\\
%   +44 (0) 20 7594 6035 \\
%   ivan.stoianov@imperial.ac.uk}
%   \cvcolumn[0.43]{Dr Edo Abraham}{Assistant Professor \\
% Department of Water Management\\
% Faculty of Civil Engineering \& Geosciences (Building 23)\\
% TU Delft\\
% Stevinweg 1, 2628 CN Delft, the Netherlands\\
% E.Abraham@tudelft.nl}
%   \end{cvcolumns}
%   \begin{cvcolumns}
%   \cvcolumn{Dr Panos Parpas}{Reader in Computational optimization\\Department of Computing\\ Imperial College London \\ 180 Queen's Gate\\
%   London SW7 2AZ\\+44 (0) 20 7594 8366\\panos.parpas@imperial.ac.uk}
% \end{cvcolumns}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
% \nocite{*}
% \bibliographystyle{plain}
% \bibliography{publications}                       % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package

\clearpage
\section*{Publications}

\subsection*{\textbf{Peer-reviewed journal articles}}
\newrefcontext[labelprefix=J]
\printbibliography[type =article]

\subsection*{\textbf{Peer-reviewed conference proceedings}}
\newrefcontext[labelprefix=C]
\printbibliography[type = inproceedings]

% \subsection*{\textbf{In preparation and submitted for publication}}
% \newrefcontext[labelprefix=S]
% \printbibliography[type = unpublished]

\subsection*{\textbf{Patents}}
\newrefcontext[labelprefix=B]
\printbibliography[type = patent]
\subsection*{\textbf{Reviews}}
\newrefcontext[labelprefix=R]
\printbibliography[type = review]
\subsection*{\textbf{Others}}
\newrefcontext[labelprefix=A]
\printbibliography[type = misc]

\subsection*{\textbf{Conference presentations}}
\small
\begin{enumerate}
\item F. Pecci, I. Stoianov.  A global optimization framework for resilient water distribution networks. International Conference on Optimization and Decision Science 2022, Florence, Italy, 30 August - 2 September, 2022.
\item F. Pecci, I. Stoianov, and A. Ostfeld. Optimal Design-for-Control of Chlorine Booster Systems in Water Networks via Convex Optimization. European Control Conference 2022, London, United Kingdom, 12-15 July, 2022.
\item I. Stoianov, F. Pecci. Mathematical optimization for intelligent water distribution networks: model calibration, and event detection and localisation. Invited seminar part of the series Control \& optimization Seminars, Imperial College London, 22 Gennaio 2020.
\item {F. Pecci}, E. Abraham, I. Stoianov. Tight Convex Relaxations for Optimal Design and Control Problems in Water distribution Networks. 17th Computing and Control for the Water Industry (CCWI), Exeter, United Kingdom, 1-4 September, 2019.
\item F. Pecci, P. Parpas, and I. Stoianov. Non-linear inverse problems via sequential convex optimization. Invited presentation at 6th International Conference on Continuous Optimization (ICCOPT), Berlin, Germany, 3 - 8 August, 2019.
\item {F. Pecci}, E. Abraham, I. Stoianov. A branch and bound method for globally optimizing valve locations in water distribution networks. 6th International Conference on Engineering Optimization (EngOpt), Lisbon, Portugal, 17 - 19 September, 2018.
\item {F. Pecci}, E. Abraham, I. Stoianov. Outer approximation methods for the solution of co-design optimization problems in water distribution networks. Invited presentation at 20th IFAC World Congress, Toulouse, France, 9 - 14 July, 2017.
\item {F. Pecci}, E. Abraham, I. Stoianov. Multiobjective pressure optimization in water distribution systems. 14th Computing and Control for the Water Industry (CCWI), Amsterdam, the Netherlands, 7-9 November, 2016 (Poster Presentation).
\item {F. Pecci}, E. Abraham, I. Stoianov. Mathematical programming methods for pressure management in water distribution systems. 13th Computing and Control for the Water Industry (CCWI), Leicester, United Kingdom, 2-4 September, 2015.
\end{enumerate}
\nocite{*}
\end{document}


%% end of file `template.tex'.
